Analysis of the 2014 Passenger Flight Network

### 2020-02-12 paper/main.tex
flow estimation results

>>>>

\begin{figure}
	\centering
	\includegraphics[width=76mm]{imgs/runway-based-estimation-problem.png}
	\caption{
For Qaanaaq Airport there was no patronage data from Wikidata and no runway information. That's why it ended up with the default patronage value 1523. In this constallation it is impossible to choose passenger flows that even remotely satisfy the the patronages of airports with ids 10, 5446, 5448}
	\label{fig:impossible_flows}
\end{figure}
